Spfy: applying a graph-based sequence database for real-time prediction of Escherichia coli phenotypes

### 2018-01-17 paper-webserver.tex
FIX: bibliography
FIX: image builds & no warnings
EDIT: emails

\bibliography{paper-webserver.bib}

%\articlesubtype{This is the article type (optional)}

@@

\title{Spfy: applying a graph-based sequence database for real-time prediction of \textit{E. coli} phenotypes}

\author[1]{Kevin K Le\thanks{kevin.le@canada.ca}}
\author[1]{Matthew D Whiteside\thanks{matthew.whiteside@canada.ca}}
\author[1]{James Hopkins}
\author[1]{Victor PJ Gannon}
\author[1]{Chad R Laing}
\affil[1]{National Microbiology Laboratory at Lethbridge, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada}

@@

\begin{figure}[t]
\begin{center}
\includegraphics{images/ontology}
\end{center}
\caption{Caption for figure within column.}
\label{fig-ontology}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics{images/results.png}
\end{center}
\caption{Caption for figure within column.}
\label{fig-results}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics{images/tables.png}
\end{center}
\caption{Caption for figure within column.}
\label{fig-tables}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics{images/docker}
\end{center}
\caption{Caption for figure within column.}
\label{fig-docker}
\end{figure}

@@

@@

\subsubsection{Conflict of interest statement.} None declared.
\newpage

\begin{thebibliography}{4}

% Format for article
\bibitem{1}
Author,A.B. and Author,C. (1992)
Article title.
\textit{Abbreviated Journal Name}, \textbf{5}, 300--330.

% Format for book
\bibitem{2}
Author,D., Author,E.F. and Author,G. (1995)
\textit{Book Title}.
Publisher Name, Publisher Address.

% Format for chapter in book
\bibitem{3}
Author,H. and Author,I. (2005)
Chapter title.
In
Editor,A. and Editor,B. (eds),
\textit{Book Title},
Publisher Name, Publisher Address,
pp.\ 60--80.

% Another article
\bibitem{4}
Author,Y. and Author,Z. (2002)
Article title.
\textit{Abbreviated Journal Name}, \textbf{53}, 500--520.

\end{thebibliography}

>>>>

%\articlesubtype{This is the article type (optional)}
% \bibliography{paper-webserver.bib}

@@

\title{Spfy: applying a graph-based sequence database for real-time prediction of Escherichia coli phenotypes}

\author[1]{Kevin K Le\thanks{kevin.le@canada.ca}}
\author[1]{Matthew D Whiteside}
\author[1]{James Hopkins}
\author[1]{Victor PJ Gannon}
\author[1]{Chad R Laing\thanks{chad.laing@canada.ca}}
\affil[1]{National Microbiology Laboratory at Lethbridge, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{images/ontology}
\end{center}
\caption{Caption for figure within column.}
\label{fig-ontology}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{images/results.png}
\end{center}
\caption{Caption for figure within column.}
\label{fig-results}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{images/tables.png}
\end{center}
\caption{Caption for figure within column.}
\label{fig-tables}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{images/docker}
\end{center}
\caption{Caption for figure within column.}
\label{fig-docker}
\end{figure}

@@

\textit{Conflict of interest}. None declared.

@@

\newpage

\bibliographystyle{unsrt}
\bibliography{paper-webserver}
